Figures for Paper

### 2021-03-26 paper_figures.Rmd

---
title: "Figures for Paper"
author: "Anna-Leigh Brown + Matteo Zanovello + Oscar Wilkins"
date: "06/10/2020"
output: 
    html_document:
        code_folding: hide
        toc: true
        toc_float: true
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
knitr::opts_chunk$set(
  comment = '', fig.width = 9, fig.height = 9
)
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load("data.table",
       "tidyverse",
       "ggplot2",
       "rcompanion",
       "lme4",
       "ggpubr",
       "forcats",
       "scales",
       "here",
       "ggthemes",
       "ggrepel",
       "DESeq2", 
       "patchwork", 
       "rstatix")
```

>>>>

---
title: "Figures for Paper"
author: "Anna-Leigh Brown + Matteo Zanovello + Oscar Wilkins"
date: "06/10/2020"
output:
    html_document:
        code_folding: hide
        toc: true
        toc_float: true
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'docs/index.html')) })
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE)
knitr::opts_chunk$set(
  comment = '', fig.width = 9, fig.height = 9
)
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load("data.table",
       "tidyverse",
       "ggplot2",
       "rcompanion",
       "lme4",
       "ggpubr",
       "forcats",
       "scales",
       "here",
       "ggthemes",
       "ggrepel",
       "DESeq2",
       "patchwork",
       "rstatix",
       "ggeasy")
```
